Designing an effective intervention of motivational interview using sequence classification methods

### 2017-02-28 paper/AMIA/main.tex
update format of table 1

\begin{table*}[htb]
\caption{Fragment of the annotated transcript of a dialogue between a counselor and an adolescent.}    
\label{table:anno_examp}
\centering
\begin{tabular}{lp{3.6cm}lp{8cm}}
\hline
\hline
Annotation  & Description & Speaker & Text \\
\hline
331 &	Open-ended question, elicit change talk positive &	Counselor &	do you feel like making healthier choices for your snacks and your meals is something you would be able to do ? mm-hmm meaning is that food available for you ? \\
117 &	Low Uptake, positive	& Adolescent &	Yes \\
301 &	Structure Session	& Counselor &	okay and thats an important thing for us to think about cause i would not want to help you come up with a plan that you would not be able to do without somebody else help so the last part of your plan is how somebody could be supportive to you meaning how they can help you be successful and so we should choose somebody who you feel like is around often enough \\
112 &	Change Talk positive	& Adolescent &	my um aunt \\
301 &	Structure Session	& Counselor &	okay so lets stick something my aunt can do \\
112 &	Change Talk positive &	Adolescent &	she could when i am doing when i am eating something that i should i could not be eating but so i can choose something healthy she could tell me not to eat it \\
309 &	Affirm, low &	Counselor &	okay that sounds like a really great suggestion \\
\hline
\hline
\end{tabular}
\end{table*}

>>>>

\begin{table}[h]
\caption{Fragment of the annotated transcript of a dialogue between a counselor and an adolescent.}    
\label{table:anno_examp}
\centering
\begin{tabular}{|l|p{3.6cm}|l|p{8cm}|}
\hline
Annotation  & Description & Speaker & Text \\\hline
331 &	Open-ended question, elicit change talk positive &	Counselor &	do you feel like making healthier choices for your snacks and your meals is something you would be able to do ? mm-hmm meaning is that food available for you ? \\\hline
117 &	Low Uptake, positive	& Adolescent &	Yes \\\hline
301 &	Structure Session	& Counselor &	okay and thats an important thing for us to think about cause i would not want to help you come up with a plan that you would not be able to do without somebody else help so the last part of your plan is how somebody could be supportive to you meaning how they can help you be successful and so we should choose somebody who you feel like is around often enough \\\hline
112 &	Change Talk positive	& Adolescent &	my um aunt \\\hline
301 &	Structure Session	& Counselor &	okay so lets stick something my aunt can do \\\hline
112 &	Change Talk positive &	Adolescent &	she could when i am doing when i am eating something that i should i could not be eating but so i can choose something healthy she could tell me not to eat it \\\hline
309 &	Affirm, low &	Counselor &	okay that sounds like a really great suggestion \\\hline
\end{tabular}
\end{table}
